Preprocessing summary

### 2018-06-19 inst/examples/summary.Rmd
ok

---
title: "Preprocessing summary"
author: "Leo Lahti"
date: "July 2, 2016"
---

@@

# Read the preprocessed data
df <- readRDS("df.Rds")
df.orig <- readRDS("df.raw.Rds")
conversions <- readRDS("conversions.Rds")
```

>>>>

---
title: "Preprocessing summary"
author: "Leo Lahti"
date: "`r date()`"
---

@@

# Read the preprocessed data
df <- readRDS("data/unified/polished/df.Rds")
df.orig <- readRDS("data/unified/polished/df.raw.Rds")
conversions <- readRDS("conversions.Rds")
```
